---
title: "homework_assignment"
output:
  html_document: default
  pdf_document: default
date: "2023-12-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# This code is loading the necessary packages for the code I will run. lsmeans is needed for my statistical analysis
install.packages("ggplot2")
install.packages("janitor")
install.packages("palmerpenguins")
install.packages("dplyr")
install.packages("lsmeans")
install_tinytex()
```
# installing the necessary data
```{r loading}
library(ggplot2)
library(palmerpenguins)
library(dplyr)
library(janitor)
library(lsmeans)
library(tinytex)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


------------------------------------------------------------------------

## QUESTION 2: Data Pipeline


### Introduction
# This plot will examine the relationship between flipper length and mass of the penguins. My hypothesis is that there is no statistically signifcant difference between flipper length relative to penguin mass when examining this between the three species. I test this by creating a scatter plot, colour coding the data by species and plotting a regression line in the data. I then compare these regression lines to determine if they differ.


```{r Data Exploration}



```



```{r}
# This code runs a set of function that clean data from my cleaning.r file. This means that I can repeatedly call on these functions instead of having to write them out mutliple times 
source("functions/cleaning.r")
source("functions/plot.r")
# Here the function clean_column_names is removing caps and spaces from the headings of my data set so that my data is easier to manipulate
names(penguins_raw)
penguins_clean <- clean_column_names(penguins_raw)
names(penguins_clean)

```

``` {r}
# This function shortens the names of the different species 
head(penguins_clean["species"])

penguins_clean_species <- shorten_species(penguins_clean)

head(penguins_clean_species["species"])
```

```{r}
# Here we are removing the empty rows from the code
penguins_plot <- remove_empty_columns_rows(penguins_clean_species)
head(penguins_plot)

```



```{r}
# This code removes all data not relevant to the plot

columns <- c("species","body_mass_g","flipper_length_mm")
penguins_plot <- subset_columns(penguins_plot,columns)
head(penguins_plot)
penguins_plot

```



```{r}
# This code plots the data subset onto a scatter graph 
# Here I have plotted body mass against flipper length and differentiated each colour by the species
# To make the graph more readable I have made the scatter points smaller and I have drawn regression lines to help visualise the data 

mass_data <- ggplot(data <- penguins_plot, aes(x = body_mass_g, y = flipper_length_mm),color = species,) + geom_point(size = 0.5,data = penguins_plot, aes(x = body_mass_g, y = flipper_length_mm, color = species)) + geom_smooth(linewidth = 0.5,method = lm, fill = NA, fullrange = TRUE, data = penguins_plot, aes(x = body_mass_g, y = flipper_length_mm, color = species)) + scale_size_manual(values = c(1,1,1),aes(x = body_mass_g, y = flipper_length_mm, color = species))
mass_data



```


### Hypothesis
# The null hypothesis is that penguins have the same flipper size relative to mass between regions. The alternative hypothesis is that flipper size is different compared to regions.

### Statistical Methods

```{r Statistics}

# Now that I have my exploratory figure. I will be statistically testing whether the slopes represented by the regression lines in the diagram are significantly different from each other using ancova. This will tell me whether different penguin species have different flipper lengths relative to their size. In this investigation I am using body mass as a proxy for the size fo the penguins



# First I create a model that considers flipper length agasint body mass and the categorical variable species, hence body_mass_g*species
model2 <- lm(flipper_length_mm ~ body_mass_g*species ,data = penguins_plot)
anova(model2) 
# Using this model I compared the regression lines of the different groups 
penguin_slopes <-lstrends(model2,"species",var="body_mass_g")
pairs(penguin_slopes)
plot(penguin_slopes)
# Make sure your code prints. 

```

### Results & Discussion

```{r Plotting Results}


penguin_slopes <-lstrends(model2,"species",var="body_mass_g")
pairs(penguin_slopes)
plot(penguin_slopes)

```

### Conclusion

# According to the results. Chinstrap and Adelie differ from each other in a statistically significant way.


